Target Markdown

### 2023-10-12 _targets.Rmd
Compute interaction plots + make simplified SEM fig

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z + rho, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{targets model-to-pred}
list(
  tar_target(model_fw_stab,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"),
      data = mutate(sim_fw, across(c(stab_com, richness), log))
      )),
  tar_target(model_fw_stab_scaled,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"
        ),
      data = sim_fw %>%
        select(-productivity) %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, richness,
              env_stoch, rho, Z,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        )
    ),
  tar_target(model_fw_stab_scaled_coeff,
    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
      as.data.frame() %>%
      rownames_to_column("term") %>%
      as_tibble() %>%
      mutate(term = str_replace(term, "cond\\.", ""))
    ),
  tar_target(pred_data, {
    to <- list(
      richness = log(seq(1, 30, 1)),
      ct_alive = c(.05, .10, .30),
      rho = c(0, .75, 1),
      avg_int_strength = c(.01, .02, .05, .1),
      env_stoch = c(.1, .6),
      w_avg_tlvl = c(1.5, 2, 3),
      Z = c(10, 100),
      h = c(2, 3),
      fw_id = NA) %>% expand.grid()
    ti <- predict(model_fw_stab,
      se.fit = TRUE, re.form = NA,
      newdata = to)
    to$stab_com <- ti$fit
    to$stab_com_se <- ti$se.fit
    to$resp_div <- rho_replacement()[as.character(to$rho)]
    to
    }),
  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(pred_sr_rho_int,
    list(
      rho = seq(0, 1, .02),
      avg_int_strength = seq(0.01, 0.2, .01)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, avg_int_strength,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .y,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100
          )
        )
      )
    )
  )
)
```

@@

```{r}
tar_make()
```

@@

```{r}

# plot just the interactions
# TODO: order by values
ti %>%
  filter(str_detect(term, ":")) %>%
  ggplot(aes(x = Estimate, y = term)) +
  geom_point()
```
```{r}
p_pred_sr_rho_int <- tar_read(pred_sr_rho_int) %>%
  ggplot(aes(x = rho, y = avg_int_strength)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg interaction strength",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
ggsave(
  here("paper", "figures", "p_pred_sr_rho_int.pdf"),
  plot = p_pred_sr_rho_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)

@@

```{r}
tar_read(sem_simplified_coeff)
```

```{r}
tar_load(sim_fw)
colnames(sim_fw)
length(unique(sim_fw$fw_id))
```

@@

```{r}
model_fw_stab <- glmmTMB(formula_stab_fw_model(
    rand_effect = TRUE,
    term_to_del = "richness : rho : Z +"),
  data = mutate(sim_fw, across(c(stab_com, richness), log))
)
diagnose(model_fw_stab)

model_fw_stab_scaled <- glmmTMB(formula_stab_fw_model(rand_effect = TRUE),
  data = sim_fw %>%
    select(-productivity) %>%
    mutate(across(c(stab_com, richness), log)) %>%
    mutate(across(c(sim_id, fw_id), as.factor)) %>%
    mutate(
      across(c(stab_com, richness,
          env_stoch, rho, Z,
          ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
        ~scale(.x)[,1])
    )
)
fixef(model_fw_stab_scaled)
diagnose(model_fw_stab_scaled)
```

```{r}
mod_tot <- lm(stab_com ~
  richness + rho + env_stoch +
  ct_alive + w_avg_tlvl + Z +
  avg_int_strength +
  h +
  richness * rho +
  richness * env_stoch +
  richness * ct_alive +
  richness * avg_int_strength +
  richness * h +
  richness * w_avg_tlvl +
  richness * Z +
  richness * rho * ct_alive +
  richness * rho * w_avg_tlvl +
  richness * rho * avg_int_strength +
  richness * rho * h +
  richness * rho * Z +
  richness * env_stoch * ct_alive +
  richness * env_stoch * Z +
  richness * env_stoch * avg_int_strength +
  richness * env_stoch * h +
  richness * env_stoch * w_avg_tlvl,
  mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
  )
```

##

>>>>

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + rho, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{targets model-to-pred}
list(
  tar_target(model_fw_stab,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"),
      data = mutate(sim_fw, across(c(stab_com, richness), log))
      )),
  tar_target(model_fw_stab_scaled,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : rho : Z +"
        ),
      data = sim_fw %>%
        select(-productivity) %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, richness,
              env_stoch, rho, Z,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        )
    ),
  tar_target(model_fw_stab_scaled_coeff,
    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
      as.data.frame() %>%
      rownames_to_column("term") %>%
      as_tibble() %>%
      mutate(term = str_replace(term, "cond\\.", ""))
    ),
  tar_target(pred_data, {
    to <- list(
      richness = log(seq(1, 30, 1)),
      ct_alive = c(.05, .10, .30),
      rho = c(0, .75, 1),
      avg_int_strength = c(.01, .02, .05, .1),
      env_stoch = c(.1, .6),
      w_avg_tlvl = c(1.5, 2, 3),
      Z = c(10, 100),
      h = c(2, 3),
      fw_id = NA) %>% expand.grid()
    ti <- predict(model_fw_stab,
      se.fit = TRUE, re.form = NA,
      newdata = to)
    to$stab_com <- ti$fit
    to$stab_com_se <- ti$se.fit
    to$resp_div <- rho_replacement()[as.character(to$rho)]
    to
    }),
  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(pred_sr_rho_int,
    list(
      rho = seq(0, 1, length.out = 50),
      avg_int_strength = seq(0.01, 0.2, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, avg_int_strength,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .y,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100))))),
  tar_target(pred_sr_rho_tlvl,
    list(
      rho = seq(0, 1, length.out = 50),
      w_avg_tlvl = seq(1.5, 3.5, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, w_avg_tlvl,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .2,
            "avg_int_strength" = .01,
            "h" = 2,
            "w_avg_tlvl" = .y,
            "Z" = 100))))),
  tar_target(pred_sr_rho_ct,
    list(
      rho = seq(0, 1, length.out = 50),
      ct_alive = seq(.02, .3, length.out = 50)
      ) %>%
    expand.grid() %>%
    mutate(
      slope_richness = map2_dbl(rho, ct_alive,
        ~get_slope_change(
          coeff = fix_fw_stab,
          gen_term = "richness",
          coeff_values = c(
            "rho" = .x,
            "env_stoch" = .1,
            "ct_alive" = .y,
            "avg_int_strength" = .01,
            "h" = 2,
            "w_avg_tlvl" = 1.5,
            "Z" = 100))))),
  tar_target(pred_sr_rho,
    map_dfr(list(pred_sr_rho_int, pred_sr_rho_ct, pred_sr_rho_tlvl),
      ~.x %>%
         pivot_longer(2, names_to = "variable", values_to = "values")
   )
  )
)
```

@@

```{r tar-make}
tar_make()
```

@@

```{r}
tar_load(model_fw_stab_scaled_coeff)

pattern <- c(var_replacement(), get_term_replacement())
names(pattern) <- paste0("\\b", names(pattern), "\\b")
```

```{r}
model_fw_stab_scaled_coeff %>%
  rename(lower_ci = `2.5 %`, upper_ci = `97.5 %`) %>%
  rename_with(tolower) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  mutate(
    type = ifelse(str_detect(term, ":"), "interaction", "single"),
    term = str_replace_all(term, pattern)
    ) %>%
  filter(type == "interaction") %>%
  ggplot(aes(x = estimate, y = term, xmin = lower_ci, xmax = upper_ci)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange() +
  labs(x = "Standardised coefficients") +
  theme_bw() +
  theme(axis.title.y = element_blank())
```

```{r}
tar_load(fix_fw_stab)
```

```{r}
pred_sr_rho_tlvl %>%
  ggplot(aes(x = rho, y = w_avg_tlvl)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg trophic level",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
```

```{r}
tar_load(pred_sr_rho)
p_pred_sr_rho <- pred_sr_rho %>%
  mutate(variable = var_replacement()[variable]) %>%
  ggplot(aes(x = rho, y = values, fill = slope_richness)) +
  geom_raster() +
  facet_wrap(~variable, scales = "free_y") +
  coord_cartesian(expand = FALSE) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Food-web structure",
    fill = "Slope Stability-Richness"
    ) +
  theme(legend.position = "bottom")
ggsave_multiple(
  paste0("p_pred_sr_rho", c(".png", ".pdf")),
  plot = p_pred_sr_rho,
  path = here::here("report", "figures"),
  scale = 2.2,
  dpi = 400,
  width = 88,
  height = 88 * .45,
  units = "mm")
```

```{r}
pred_sr_rho_ct %>%
  ggplot(aes(x = rho, y = ct_alive)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg trophic level",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
```

```{r}
p_pred_sr_rho_int <- tar_read(pred_sr_rho_int) %>%
  ggplot(aes(x = rho, y = avg_int_strength)) +
  geom_raster(aes(fill = slope_richness)) +
  scale_fill_gradient2(
    low = "red",
    mid = "white",
    high = "blue",
    midpoint = 0,
    space = "Lab",
    na.value = "grey50",
    guide = "colourbar",
    aesthetics = "fill") +
  labs(
    x = "Environmental correlation",
    y = "Avg interaction strength",
    fill = "Slope Stability-Richness"
  ) +
theme(legend.position = "bottom")
ggsave(
  here("paper", "figures", "p_pred_sr_rho_int.pdf"),
  plot = p_pred_sr_rho_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)

@@

```{r}
tar_read(sem_simplified_coeff) %>%
  filter(abs(Std.Estimate) > .1) %>%
  janitor::clean_names() %>%
  mutate(std_estimate = round(std_estimate, 1))
tar_read(sem_simplified_rsquared) %>%
  janitor::clean_names() %>%
  mutate(r_squared = round(r_squared, 2))
```

@@
